Trends of SDR in Thessaloniki

### 2023-07-02 Article.Rmd
Commit 2023-07-02 15:17

# Data and methodology.

<!-- time span -->
The SDR is equivalent to the whole sky Global radiation (or Global Horizontal Irradiance, GHI), and was obtained with a horizontal leveled, CM-21 pyranometer, from \mbox{`r min(ALL_1_daily_DESEAS$Date)`} to \mbox{`r max(ALL_1_daily_DESEAS$Date)`}.
Also, we have measurements of direct beam radiation (DNI) obtained by a collocated CHP-1 pyrheliometer, from \mbox{`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`} to \mbox{`r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`}

In some algorithms, we used as auxiliary data, the direct beam radiation (DNI) for comparisons, obtained by a CHP-1 pyrheliometer, with data availability from  
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` to `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.

>>>>

# Observational data and methodology.

<!-- time span -->
The SDR is equivalent to the whole sky Global radiation (or Global Horizontal Irradiance, GHI), and was obtained with a horizontal leveled, CM-21 pyranometer, from 
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS$Date)`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS$Date)`.
<!-- }. -->
Also, we have measurements of direct beam radiation (DNI) obtained by a collocated CHP-1 pyrheliometer, from 
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.
<!-- }. -->
Although, we performed similar analysis to DNI as for SDR, due to the sorter duration of the data, the results are not presented here, as they lack the appropriate statistical significance.

Moreover, the DNI was used as auxiliary data, with the clear sky identification algorithm (CSid), to aid with the selection of the appropriate thresholds. 
We have to note that, despite the capability of the CSid to use the DNI as an characterization parameter,

.... wi dindnt use it  .....

but was not used as indicator of clear sky instances
